Additional analyses

### 2022-04-11 analyses.RmD
- updated figures

@@

  if(isTRUE(class(data_aff_neg) == "lmerModLmerTest")) {
         dat_fig_results <- 
           broom.mixed::tidy(data_aff_neg, conf.int = T) %>% 
           mutate(dv = "aff_neg") %>% 
           rbind(
             broom.mixed::tidy(data_aff_pos, conf.int = T) %>% 
               mutate(dv = "aff_pos")) %>% 
           rbind(
             broom.mixed::tidy(data_life_sat, conf.int = T) %>% 
               mutate(dv = "life_sat"))
         } else{ 
           dat_fig_results <- 
             data_aff_neg %>% 
             mutate(dv = "aff_neg") %>% 
             rbind(data_aff_pos %>% 
                   mutate(dv = "aff_pos")) %>% 
             rbind(data_life_sat %>% 
                     mutate(dv = "life_sat")) %>% 
           rename(conf.low = `2.5 %`, conf.high = `97.5 %`)
           }
  dat_fig_results %<>% 
  mutate(
    type = ifelse(grepl(".*_w\\>", .$term), "within", "between"),
    iv = gsub("_(w|b)\\>", "", .$term)
         ) %>%
  mutate(
    type = factor(.$type, 
                  levels = c("within", "between")),
    dv = factor(.$dv, 
                levels = c("life_sat", "aff_pos", "aff_neg"),
                labels = c("Life satisfaction", "Positive affect", "Negative affect")),
    analysis = analysis
  ) %>% 
  select(dv, iv, type, analysis, estimate, conf.low, conf.high, p.value)

@@

```{r}
make_graph_res <- function(data, sesoi = NULL, legend = TRUE){
  ggplot(data, aes(x = estimate, y = iv)) + 
  scale_color_manual(values = c("grey40", "deepskyblue", "darkcyan", "cornflowerblue", "aquamarine")) +
  geom_vline(xintercept = 0, lwd = .75, colour = "darkgrey") + 
  geom_errorbarh(aes(xmin = conf.low, xmax = conf.high, color = analysis),
                lwd = .75, height = .2, position = position_dodge(.5)) +
  geom_point(aes(color = analysis), size = 2, position = position_dodge(.5)) +
  {if(isTRUE(sesoi == "est")) geom_vline(data=filter(data, dv=="Life satisfaction"), aes(xintercept=-.3), colour="darkgrey", linetype = "dashed")} + 
    {if(isTRUE(sesoi == "est")) geom_vline(data=filter(data, dv=="Life satisfaction"), aes(xintercept=.3), colour="darkgrey", linetype = "dashed")} + 
  {if(isTRUE(sesoi == "est")) geom_vline(data=filter(data, dv!="Life satisfaction"), aes(xintercept=-.15), colour="darkgrey", linetype = "dashed")} +
    {if(isTRUE(sesoi == "est")) geom_vline(data=filter(data, dv!="Life satisfaction"), aes(xintercept=.15), colour="darkgrey", linetype = "dashed")} +
  {if(isTRUE(sesoi == "std")) geom_vline(aes(xintercept=.1), colour="darkgrey", linetype = "dashed")} + 
  {if(isTRUE(sesoi == "std")) geom_vline(aes(xintercept=-.1), colour="darkgrey", linetype = "dashed")} +   
    theme(
    axis.title.y = element_blank(),
    plot.title = element_text(hjust = .5),
    panel.spacing = unit(.9, "lines"),
    text = element_text(size = 12),
    axis.text.y = element_text(hjust = 0)
    ) +
  {if(!isTRUE(legend)) theme(legend.position = "none")} + 
  guides(colour = guide_legend(reverse=T)) +
  facet_grid(rows = vars(type),
             cols = vars(dv),
             scales = "free",
             space = "free_y") 
}
```

@@

Determine amount of missingness per respondent per wave. Because calculation takes long, this chunk is not executed but loaded from memory. To execute, set eval == TRUE.

@@

Load imputed data from disc.

```{r}
d_long_imp <- read_csv("data/data_imputed.csv")
```

@@

# Analyses
## Life satisfaction

First, without control variables.

@@

Now with control variables.

## Positive Affect

First, without control variables.

@@

Now with control variables.

## Negative Affect

First, without control variables.

@@

Then, with control variables.

@@

First, for activities.

```{r}
# get data
dat_fig_results_activity <- get_dat_res(model_aff_neg_lmer, model_aff_pos_lmer, model_life_sat_lmer, 
                                        type = "activity", analysis = "regular")
dat_fig_results_activity_nco <- get_dat_res(model_aff_neg_lmer_nco, model_aff_pos_lmer_nco, model_life_sat_lmer_nco, 
                                            type = "activity", analysis = "no controls")
dat_fig_results_activity <- rbind(
  dat_fig_results_activity, 
  dat_fig_results_activity_nco
)

@@

Then for channels.

```{r}
# get data
dat_fig_results_channels <- get_dat_res(model_aff_neg_lmer, model_aff_pos_lmer, model_life_sat_lmer, 
                                        type = "channels", analysis = "regular")
dat_fig_results_channels_nco <- get_dat_res(model_aff_neg_lmer_nco, model_aff_pos_lmer_nco, model_life_sat_lmer_nco, 
                                            type = "channels", analysis = "no controls")
dat_fig_results_channels <- rbind(
  dat_fig_results_channels, 
  dat_fig_results_channels_nco
)

@@

Select control variables and make graph.

```{r}
# make figure
fig_results_control <- make_graph_res(
  get_dat_res(model_aff_neg_lmer, model_aff_pos_lmer, model_life_sat_lmer, analysis = "exploratory", type = "control"),
  legend = FALSE
  )
fig_results_control

# save figure
ggsave("figures/fig_results_control.pdf", 
       width = 7, height = 4,
       plot = fig_results_control)
```

>>>>

## Session info

Provide session info to make results reproducible.

```{r}
sessionInfo()
```

@@

  if(isTRUE(class(data_aff_neg) == "lmerModLmerTest")) {
         dat_fig_results <- 
           broom.mixed::tidy(data_aff_neg, conf.int = T) %>% 
           mutate(dv = "aff_neg") %>% 
           rbind(
             broom.mixed::tidy(data_aff_pos, conf.int = T) %>% 
               mutate(dv = "aff_pos")) %>% 
           rbind(
             broom.mixed::tidy(data_life_sat, conf.int = T) %>% 
               mutate(dv = "life_sat"))
         } else{ 
           dat_fig_results <- 
             data_aff_neg %>% 
             mutate(dv = "aff_neg") %>% 
             rbind(data_aff_pos %>% 
                   mutate(dv = "aff_pos")) %>% 
             rbind(data_life_sat %>% 
                     mutate(dv = "life_sat")) %>% 
           rename(conf.low = `2.5 %`, conf.high = `97.5 %`)
           }
  dat_fig_results %<>% 
  mutate(
    type = ifelse(grepl(".*_w\\>", .$term), "within", "between"),
    iv = gsub("_(w|b)\\>", "", .$term)
         ) %>%
  mutate(
    type = factor(.$type, 
                  levels = c("within", "between")),
    dv = factor(.$dv, 
                levels = c("life_sat", "aff_pos", "aff_neg"),
                labels = c("Life satisfaction", "Positive affect", "Negative affect")),
    Analysis = analysis
  ) %>% 
  select(dv, iv, type, Analysis, estimate, conf.low, conf.high, p.value)

@@

```{r}
make_graph_res <- function(data, sesoi = NULL, legend = TRUE){
  ggplot(data, aes(x = estimate, y = iv)) + 
  scale_color_manual(values = c("black", "grey60", "grey75", "deepskyblue", "cornflowerblue", "darkcyan", "aquamarine")) +
  geom_vline(xintercept = 0, lwd = .75, colour = "darkgrey") + 
  geom_errorbarh(aes(xmin = conf.low, xmax = conf.high, color = Analysis),
                lwd = .75, height = .2, position = position_dodge(-.7)) +
  geom_point(aes(color = Analysis), size = 2, position = position_dodge(-.7)) +
  {if(isTRUE(sesoi == "est")) geom_vline(data=filter(data, dv=="Life satisfaction"), aes(xintercept=-.3), colour="darkgrey", linetype = "dashed")} + 
    {if(isTRUE(sesoi == "est")) geom_vline(data=filter(data, dv=="Life satisfaction"), aes(xintercept=.3), colour="darkgrey", linetype = "dashed")} + 
  {if(isTRUE(sesoi == "est")) geom_vline(data=filter(data, dv!="Life satisfaction"), aes(xintercept=-.15), colour="darkgrey", linetype = "dashed")} +
    {if(isTRUE(sesoi == "est")) geom_vline(data=filter(data, dv!="Life satisfaction"), aes(xintercept=.15), colour="darkgrey", linetype = "dashed")} +
  {if(isTRUE(sesoi == "std")) geom_vline(aes(xintercept=.1), colour="darkgrey", linetype = "dashed")} + 
  {if(isTRUE(sesoi == "std")) geom_vline(aes(xintercept=-.1), colour="darkgrey", linetype = "dashed")} +   
    theme(
    axis.title.y = element_blank(),
    plot.title = element_text(hjust = .5),
    panel.spacing = unit(.9, "lines"),
    text = element_text(size = 12),
    axis.text.y = element_text(hjust = 0)
    ) +
  {if(!isTRUE(legend)) theme(legend.position = "none")} + 
  # guides(colour = guide_legend(reverse=T)) +
  facet_grid(rows = vars(type),
             cols = vars(dv),
             scales = "free",
             space = "free_y") 
}
```

@@

Determine amount of missingness per respondent per wave. Because calculation takes long, this chunk is loaded from memory.

@@

```{r eval=FALSE}
# to further increase speed, you can also load the imputed data from the directory
d_long_imp <- read_csv("data/data_imputed.csv")
```

@@

# Analyses
## Preregistered
### Life satisfaction

### Positive Affect

### Negative Affect

## Without control variables
### Life Satisfaction

@@

### Positive Affect

@@

### Negative Affect

@@

## Standardized results

First, create standardized dataset.

```{r}
d_long_std <- d_long_imp %>% 
  mutate(across(c(-id, -wave, -gender, -male, -born_aus, -born_aus_prnts, -edu_fac, -employment_fac, -res_vienna, -acc_bal, -acc_gar), scale))
```

Then let's rerun the analyses.

### Life satisfaction

```{r}
model_life_sat_lmer_std <- lmerTest::lmer(life_sat ~
                                        (1 | id) + (1 | wave) + 
                                        soc_med_read_w + soc_med_like_share_w + soc_med_post_w  + 
                                        soc_med_fb_w + soc_med_ig_w + soc_med_wa_w + soc_med_yt_w + soc_med_tw_w +
                                        soc_med_read_b + soc_med_like_share_b + soc_med_post_b + 
                                        soc_med_fb_b + soc_med_ig_b + soc_med_wa_b + soc_med_yt_b + soc_med_tw_b +  
                                        age + male + born_aus + born_aus_prnts + edu_fac + employment_fac + health_b + 
                                        res_vienna + acc_bal + acc_gar + home_sqm + 
                                        med_txt_kro_b + med_txt_sta_b + med_txt_pre_b + med_txt_oes_b + med_txt_kur_b + med_txt_slz_b + med_txt_son_b + 
                                        med_vid_orf_b + med_vid_pri_b + 
                                        risk_prop_b + loc_cntrl_int_m_b + 
                                        act_wrk_w + act_spo_w + act_frn_w + act_sho_w + act_pet_w + 
                                        act_wrk_b + act_spo_b + act_frn_b + act_sho_b + act_pet_b +
                                        sat_dem_w + sat_dem_b 
                                      , data = d_long_std)
summary(model_life_sat_lmer_std)
```

```{r}
model_aff_pos_lmer_std <- lmerTest::lmer(aff_pos_fs ~ 
                                        (1 | id) + (1 | wave) + 
                                        soc_med_read_w + soc_med_like_share_w + soc_med_post_w + 
                                        soc_med_fb_w + soc_med_ig_w + soc_med_wa_w + soc_med_yt_w + soc_med_tw_w +
                                        soc_med_read_b + soc_med_like_share_b + soc_med_post_b + 
                                        soc_med_fb_b + soc_med_ig_b + soc_med_wa_b + soc_med_yt_b + soc_med_tw_b +  
                                        age + male + born_aus + born_aus_prnts + edu_fac + employment_fac + health_b + 
                                        res_vienna + acc_bal + acc_gar + home_sqm + 
                                        med_txt_kro_b + med_txt_sta_b + med_txt_pre_b + med_txt_oes_b + med_txt_kur_b + med_txt_slz_b + med_txt_son_b + 
                                        med_vid_orf_b + med_vid_pri_b + 
                                        risk_prop_b + loc_cntrl_int_m_b + 
                                        act_wrk_w + act_spo_w + act_frn_w + act_sho_w + act_pet_w + 
                                        act_wrk_b + act_spo_b + act_frn_b + act_sho_b + act_pet_b +
                                        sat_dem_w + sat_dem_b 
                                      , data = d_long_imp)
summary(model_aff_pos_lmer_std)
```

### Negative Affect

```{r}
model_aff_neg_lmer_std <- lmerTest::lmer(aff_neg_fs ~ 
                                        (1 | id) + (1 | wave) + 
                                        soc_med_read_w + soc_med_like_share_w + soc_med_post_w + 
                                        soc_med_fb_w + soc_med_ig_w + soc_med_wa_w + soc_med_yt_w + soc_med_tw_w +
                                        soc_med_read_b + soc_med_like_share_b + soc_med_post_b + 
                                        soc_med_fb_b + soc_med_ig_b + soc_med_wa_b + soc_med_yt_b + soc_med_tw_b +  
                                        age + male + born_aus + born_aus_prnts + edu_fac + employment_fac + health_b + 
                                        res_vienna + acc_bal + acc_gar + home_sqm + 
                                        med_txt_kro_b + med_txt_sta_b + med_txt_pre_b + med_txt_oes_b + med_txt_kur_b + med_txt_slz_b + med_txt_son_b + 
                                        med_vid_orf_b + med_vid_pri_b + 
                                        risk_prop_b + loc_cntrl_int_m_b + 
                                        act_wrk_w + act_spo_w + act_frn_w + act_sho_w + act_pet_w + 
                                        act_wrk_b + act_spo_b + act_frn_b + act_sho_b + act_pet_b +
                                        sat_dem_w + sat_dem_b 
                                      , data = d_long_imp)
summary(model_aff_neg_lmer_std)
```

@@

## Activities

```{r}
# get data
dat_fig_results_activity <- get_dat_res(model_aff_neg_lmer, model_aff_pos_lmer, model_life_sat_lmer, 
                                        type = "activity", analysis = "regular")
dat_fig_results_activity_nco <- get_dat_res(model_aff_neg_lmer_nco, model_aff_pos_lmer_nco, model_life_sat_lmer_nco, 
                                            type = "activity", analysis = "no controls")
dat_fig_results_activity_std <- get_dat_res(model_aff_neg_lmer_std, model_aff_pos_lmer_std, model_life_sat_lmer_std, 
                                            type = "activity", analysis = "standardized")

dat_fig_results_activity <- rbind(
  dat_fig_results_activity, 
  dat_fig_results_activity_nco,
  dat_fig_results_activity_std
) %>% 
  mutate(Analysis = factor(Analysis, levels = c("regular", "no controls", "standardized")))

@@

## Channels

```{r}
# get data
dat_fig_results_channels <- get_dat_res(model_aff_neg_lmer, model_aff_pos_lmer, model_life_sat_lmer, 
                                        type = "channels", analysis = "regular")
dat_fig_results_channels_nco <- get_dat_res(model_aff_neg_lmer_nco, model_aff_pos_lmer_nco, model_life_sat_lmer_nco, 
                                            type = "channels", analysis = "no controls")
dat_fig_results_channels_std <- get_dat_res(model_aff_neg_lmer_std, model_aff_pos_lmer_std, model_life_sat_lmer_std, 
                                            type = "channels", analysis = "standardized")

dat_fig_results_channels <- rbind(
  dat_fig_results_channels, 
  dat_fig_results_channels_nco,
  dat_fig_results_channels_std
) %>% 
  mutate(Analysis = factor(Analysis, levels = c("regular", "no controls", "standardized")))

@@

## Selected control variables

Standardized, to allow for better comparison across differently scaled variables.

```{r}
# make figure
fig_results_control_std <- make_graph_res(
  get_dat_res(model_aff_neg_lmer_std, model_aff_pos_lmer_std, model_life_sat_lmer_std, 
              type = "control", analysis = "standardized"),
  sesoi = "std",
  legend = FALSE
  )
fig_results_control_std

# save figure
ggsave("figures/fig_results_control_std.pdf", 
       width = 7, height = 4,
       plot = fig_results_control_std)
```

### 2022-04-11 analyses_additional.Rmd
- updated figures

Here you can find the code and the results of all additional analyses. To see the code, click on button "Code". Alternatively, you can download the rmd file from the github repo.

@@

Load packages, and make repo replicable.

@@

# Standardized results

First, create standardized dataset.

```{r}
d_long_std <- d_long_imp %>% 
  mutate(across(c(-id, -wave, -gender, -male, -born_aus, -born_aus_prnts, -edu_fac, -employment_fac, -res_vienna, -acc_bal, -acc_gar), scale))
```

Then let's rerun the analyses.

```{r}
model_life_sat_lmer_std <- lmerTest::lmer(life_sat ~
                                        (1 | id) + (1 | wave) + 
                                        soc_med_read_w + soc_med_like_share_w + soc_med_post_w  + 
                                        soc_med_fb_w + soc_med_ig_w + soc_med_wa_w + soc_med_yt_w + soc_med_tw_w +
                                        soc_med_read_b + soc_med_like_share_b + soc_med_post_b + 
                                        soc_med_fb_b + soc_med_ig_b + soc_med_wa_b + soc_med_yt_b + soc_med_tw_b +  
                                        age + male + born_aus + born_aus_prnts + edu_fac + employment_fac + health_b + 
                                        res_vienna + acc_bal + acc_gar + home_sqm + 
                                        med_txt_kro_b + med_txt_sta_b + med_txt_pre_b + med_txt_oes_b + med_txt_kur_b + med_txt_slz_b + med_txt_son_b + 
                                        med_vid_orf_b + med_vid_pri_b + 
                                        risk_prop_b + loc_cntrl_int_m_b + 
                                        act_wrk_w + act_spo_w + act_frn_w + act_sho_w + act_pet_w + 
                                        act_wrk_b + act_spo_b + act_frn_b + act_sho_b + act_pet_b +
                                        sat_dem_w + sat_dem_b 
                                      , data = d_long_std)
summary(model_life_sat_lmer_std)
```

```{r}
model_aff_pos_lmer_std <- lmerTest::lmer(aff_pos_fs ~ 
                                        (1 | id) + (1 | wave) + 
                                        soc_med_read_w + soc_med_like_share_w + soc_med_post_w + 
                                        soc_med_fb_w + soc_med_ig_w + soc_med_wa_w + soc_med_yt_w + soc_med_tw_w +
                                        soc_med_read_b + soc_med_like_share_b + soc_med_post_b + 
                                        soc_med_fb_b + soc_med_ig_b + soc_med_wa_b + soc_med_yt_b + soc_med_tw_b +  
                                        age + male + born_aus + born_aus_prnts + edu_fac + employment_fac + health_b + 
                                        res_vienna + acc_bal + acc_gar + home_sqm + 
                                        med_txt_kro_b + med_txt_sta_b + med_txt_pre_b + med_txt_oes_b + med_txt_kur_b + med_txt_slz_b + med_txt_son_b + 
                                        med_vid_orf_b + med_vid_pri_b + 
                                        risk_prop_b + loc_cntrl_int_m_b + 
                                        act_wrk_w + act_spo_w + act_frn_w + act_sho_w + act_pet_w + 
                                        act_wrk_b + act_spo_b + act_frn_b + act_sho_b + act_pet_b +
                                        sat_dem_w + sat_dem_b 
                                      , data = d_long_imp)
summary(model_aff_pos_lmer_std)
```

```{r}
model_aff_neg_lmer_std <- lmerTest::lmer(aff_neg_fs ~ 
                                        (1 | id) + (1 | wave) + 
                                        soc_med_read_w + soc_med_like_share_w + soc_med_post_w + 
                                        soc_med_fb_w + soc_med_ig_w + soc_med_wa_w + soc_med_yt_w + soc_med_tw_w +
                                        soc_med_read_b + soc_med_like_share_b + soc_med_post_b + 
                                        soc_med_fb_b + soc_med_ig_b + soc_med_wa_b + soc_med_yt_b + soc_med_tw_b +  
                                        age + male + born_aus + born_aus_prnts + edu_fac + employment_fac + health_b + 
                                        res_vienna + acc_bal + acc_gar + home_sqm + 
                                        med_txt_kro_b + med_txt_sta_b + med_txt_pre_b + med_txt_oes_b + med_txt_kur_b + med_txt_slz_b + med_txt_son_b + 
                                        med_vid_orf_b + med_vid_pri_b + 
                                        risk_prop_b + loc_cntrl_int_m_b + 
                                        act_wrk_w + act_spo_w + act_frn_w + act_sho_w + act_pet_w + 
                                        act_wrk_b + act_spo_b + act_frn_b + act_sho_b + act_pet_b +
                                        sat_dem_w + sat_dem_b 
                                      , data = d_long_imp)
summary(model_aff_neg_lmer_std)
```

@@

# Figures
## Standardized results

First, for activities.

```{r}
# make figure
fig_results_activity_std <- make_graph_res(
  get_dat_res(model_aff_neg_lmer_std, model_aff_pos_lmer_std, model_life_sat_lmer_std, 
              type = "activity", analysis = "standardized"),
  sesoi = "std",
  legend = FALSE
  )
fig_results_activity_std

# safe figure
ggsave("figures/fig_results_activity_std.pdf", 
       width = 7, height = 4,
       plot = fig_results_activity_std)
```

Then for channels.

```{r}
# make figure
fig_results_channels_std <- make_graph_res(
  get_dat_res(model_aff_neg_lmer_std, model_aff_pos_lmer_std, model_life_sat_lmer_std, type = "channels", analysis = "standardized"),
  sesoi = "std",
  legend
  )
fig_results_channels_std

# save figure
ggsave("figures/fig_results_channels_std.pdf", 
       width = 7, height = 4,
       plot = fig_results_channels_std)
```

Select control variables and make graph.

```{r}
# make figure
fig_results_control_std <- make_graph_res(
  get_dat_res(model_aff_neg_lmer_std, model_aff_pos_lmer_std, model_life_sat_lmer_std, 
              type = "control", analysis = "standardized"),
  sesoi = "std"
  )
fig_results_control_std

# save figure
ggsave("figures/fig_results_control_std.pdf", 
       width = 7, height = 4,
       plot = fig_results_control_std)
```

## Comparison of unstandardized methods

In what follows, see figure with all results combined. Only nonstandardized results are presented to use the same scaling.

First, for activities.

@@

Then for channels.

>>>>

 - Here you can find the code and the results of all additional analyses. 
 - To see the results, I recommend you directly go down to the Figures section. 
 - But if you're interested in how the analyses were executed, just tag along.
 - To see the code, click on button "Code". Alternatively, you can download the rmd file from the github repo.
 - To execute the code, first download the actual data from AUSSDA, then run analysis.rmd, then this file

@@

Load packages.

@@

@@

# Figures

In what follows, see figure with all results combined.

## Activities

@@

## Channels
